### 2018-10-29 Sections/economics_of_the_quantum_internet.tex
Subjective vs objective value of comp

@@

As discussed in relation to combined computational scaling functions (Sec.~\ref{sec:comb_comp_sc_func})\index{Combined computational scaling functions}, different market participants will be executing different software applications on their share of the quantum computing resources, with differing QCLs\index{Quantum computational leverage}. Because the applications differ between users, as do their QCLs, so too does the monetary value of the computations they are performing. This yields the distinction between \textit{subjective}\index{Subjective value of computation} and \textit{objective}\index{Objective value of computation} value of computation.

The subjective value of a computation is the value to an end-user of a computation, measured in terms of their associated monetary profit from utilising its output. The objective value, rather, is the cost of the hardware, which is not application-specific.

The question then is how to reconcile the distinction between subjective and objective value, given the diversity of applications in the quantum marketplace. This will supersede the na\"ive models for cost of computation presented earlier, which were based entirely on objective value. Of course, subjective value is what people are actually willing to pay for in the real-world!

>>>>

%
% Subjective vs Objective Value of Computation
%

\subsection{Subjective vs. objective value of computation}\index{Subjective value of computation}\index{Objective value of computation}\label{sec:sub_vs_obj}

As discussed in relation to combined computational scaling functions (Sec.~\ref{sec:comb_comp_sc_func})\index{Combined computational scaling functions}, different market participants will be executing different software applications on their share of the quantum computing resources, with differing QCLs\index{Quantum computational leverage}. Because the applications differ between users, as do their QCLs, so too does the monetary value of the computations they are performing. This yields the distinction between \textit{subjective}\index{Subjective value of computation} and \textit{objective}\index{Objective value of computation} value of computation:

\begin{itemize}
\item Subjective value of computation: the value to an end-user of a computation, measured in terms of their associated monetary profit from utilising its output, which is highly application-specific.
\item Objective value of computation: the cost of the physical hardware and infrastructure, which is not application-specific.
\end{itemize}

@@

In light of the distinction between subjective and objective value of computation, the question  is how to reconcile this distinction in value, given the diversity of applications in the quantum marketplace. This will supersede the na\"ive models for cost of computation presented earlier, which were based entirely on objective value. Of course, subjective value is what people are actually willing to pay for in the real-world!
